---
title: "final_project"
author: "Asha Yadav"
date: "2/22/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Datasets

```{r data}

library(tidyverse)
library(rio)
library(here)
library(naniar)

# Loading data

NCSH <- import(here("data","2017-2018 NSCH_Topical_DRC_Dec 2019.csv"))
state <- import(here("data","fips_state.csv"))

#The above code did not work, I got an error telling me there was no such file in the directory

NCSH <- read_csv("2017-2018 NSCH_Topical_DRC_Dec 2019.csv")
state <- read_csv("fips_state.csv")

# Left_join to add states in the NCSH dataset

final_data <- left_join(NCSH, state, by = "FIPSST")

```

2. Plot 1: Used the raw data

```{r fig.width=20}

final_data_2 <- final_data%>%
  select(State, SC_CSHCN, ACE2more_1718)
final_data_2$SC_CSHCN[which(final_data_2$SC_CSHCN==1)]<-"Sp Health Needs"
final_data_2$SC_CSHCN[which(final_data_2$SC_CSHCN==2)]<-"No Sp Health needs"

final_data_2$ACE2more_1718[which(final_data_2$ACE2more_1718==1)]<-"Exp No ACE"
final_data_2$ACE2more_1718[which(final_data_2$ACE2more_1718==2)]<-"Exp 1 ACE"
final_data_2$ACE2more_1718[which(final_data_2$ACE2more_1718==3)]<-"Exp 2 ACE"

final_data_2 <- final_data_2%>%
  replace_with_na(replace = list(ACE2more_1718 = 99))%>%
  drop_na()%>%
  group_by(State, SC_CSHCN)%>%
  count(ACE2more_1718)

ggplot(final_data_2, aes(x = ACE2more_1718, 
                         y = n, 
                         fill = SC_CSHCN)) +
  geom_col(position = "dodge") +
  coord_flip() +
  facet_wrap(~State)

#Wow, so much data! Could you just plot a subset of states?

```


3. Plot 2: Calculated proportion of type of adverse childhood experience.

```{r, fig.width=20}

final_data_3 <- final_data_2%>%
  mutate(proportion = (n/sum(n)))

ggplot(final_data_3, aes(x = ACE2more_1718, 
                         y = proportion, 
                         fill = SC_CSHCN)) +
  geom_col(position = "dodge") +
  coord_flip() +
  facet_wrap(~State)

#Again, this is so much data, I don't know what to focus on.
#Aesthetically, could you use different colors?
#clean up labels
#Instead of the default, xould you have the titles for the facets be on white background, without the black outline?

```

4. Plot 3: Clearer version

```{r fig.width=20, fig.height=30}

final_data_3 <- final_data_2%>%
  mutate(percentage = (n/sum(n))*100)

ggplot(final_data_3, aes(x = ACE2more_1718, 
                         y = percentage, 
                         fill = SC_CSHCN)) +
  geom_col(position = "dodge") +
  coord_flip() +
  facet_wrap(~State) +
  theme(strip.text.x = element_text(size=20),
        strip.background = element_rect(color = "black"),
        legend.position = c(.85, .1),
        axis.title.x = element_blank(),
        axis.title.y = element_blank(),
        text = element_text(size = 30),
        legend.title = element_blank()) +
  labs(title = "Children with special health needs likely to experience higher adverse childhood\nexperiences in United States\n",
       caption = "Data Source: NSCH 2017-18 data")

#Same issues, this graph is not legible without zoom.
#Since you are looking at a difference in this plot, instead of showing adverse childhood experience for both groups in parallel bars, could you just calculate the difference between the groups and plot that?

```

I think you have some really interesting and important data that needs to be communicated. Looig forward, I wonder how you can make the data more accessible.
Focussing on certain regions over others might be an easy way to do it. Alternatively, you could focus on those states where children have the most adverse experiences.

Also, since you have regional data, I think it would be a great occasion to use a geographic map. That would be a fun alternative to the barcharts.

